### 2024-08-16 machine-learning.qmd
Built site for gh-pages

When performing machine learning, there may be multiple approaches you can take to address this:

- transforming data from [long to wide](#sec-longToWide) form, so that each person has only one row
- when designing the training and test sets, keep all measurements from the same person in the same data object (either the training or test set); do not have some measurements from a given person in the training set and other measurements from the same person in the test set
- use a machine learning approach that accounts for the clustered/nested nature of the data

>>>>

When performing machine learning, various approaches may help address this:

- transform data from [long to wide](#sec-longToWide) form, so that each person has only one row
- when designing the training and test sets, keep all measurements from the same person in the same data object (either the training or test set); do not have some measurements from a given person in the training set and other measurements from the same person in the test set
- use a machine learning approach that accounts for the clustered/nested nature of the data
